---
title: "Single salt"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Loading af pakker 
library(dplyr)
library(tidyr)
library(ggplot2)
library(visdat)
library(GGally)
library(Hmisc)
library(DMwR2)
library(data.table)
library(mltools)
library(ggfortify)
library(ggiraphExtra)
library(coronavirus)
library(lubridate)
library(plotly)
library(readxl)
require(readr)
library(zoo)
library(latex2exp)
library(fs)
```

Summary of single salt experiments.

All experiments were performed with:

Flux 20 LMH (permeate flow 17 mL/min)

Crossflow of 0.5 m/s (feed flow 1160 mL/min) 

Initial feed volume of 6L. 

The concentraiton of the various salts were selected based on concentration of authentic CT reservior water. 

<h3> NaCl </h3>
The first single salt experiment performed was with 3mM NaCl concentration.
The water recoveyr for this experiment is 88.6 %
Where the pressure was logged before and after the the membrane and the TMP was calculated. 
There is many fluctuations in the data due to insufficient regulations of the regulation pressure valve. 
The larger pressure fluctuations after 1 h, 2h, 3.5h is due to sampling from the permeate stream, which disrupts the automatic pressure regulation.
The TMP decrease slightly from 2.5 bar to 2.3 bar over the time duration of 4 hours. 

```{R NaCl import data plot pressure, echo=FALSE, message=FALSE}
### NaCl 3 mM
CWF_NaCl = read_delim("data/singlesalt_NaCl3mM_14-09-2021.csv",delim = "\t", escape_double = FALSE, 
                  trim_ws = TRUE, skip = 5) #Hente data og få det til passe ned i en tabel
#str(CWF)
dat_NaCl = as.data.frame(CWF_NaCl) #Ændrer strukturen af dataen til noget vi kan arbejde med
old_names=colnames(CWF_NaCl) #Vi finder de latterlige navne kolonnerne i dataen har 
new_names=c("time","level","con0201","pH0201","con0301","flow0301",
            "p0301","p0302","p0401","flow0401","p0501","con0501",
            "temp0501","p0601","temp0601","16","17","18","19","20",
            "21","pmp0201","pmp0301","pmp0401","pmp0501","flow_avg0301",
            "p_avg0301","p_avg0302","p_avg0401","flow_avg0401",
            "p_avg0501","FT0302","weight0302","flow0501","weight0501","36","pH0301",
            "pH0501","con0302","40") #Vi finder på nogle lidt bedre nogle
dat_NaCl = dat_NaCl %>% rename_at(vars(old_names),~new_names) #Vi ændrer navnene til de nye
dat_NaCl$time = dmy_hms(dat_NaCl$time)#Vi ændrer formatet af 'dato' kolonnen til et standard format for tid og datoer istedet for at det bare er noget tekst
#str(dat)


#tid_sec <- as.numeric(as.POSIXct(dat_NaCl$time))-as.numeric(as.POSIXct("2021-09-14 11:16:26", format='%Y-%m-%d %H:%M:%S')) #den regner 2 timer for meget, tag højde for det manuelt checket hvornår flow rammer 17 ml/min. 
#dat_NaCl <- data.frame(dat_NaCl,tid_sec) #tilføjer tid til data.frame

### Finde t=0 (fosøgsstart = der hvor flow er over 16 mL/min)
flow_boolean = dat_NaCl$flow0501>16&dat_NaCl$flow0501<25
start_tid = min(which(flow_boolean))
dat_NaCl=dat_NaCl[-c(1:start_tid),]
flow_boolean_slut = dat_NaCl$flow0501<1
slut_tid = min(which(flow_boolean_slut))
dat_NaCl=dat_NaCl[-c(slut_tid:(nrow(dat_NaCl)) ),]
### Tid i s fra forsøgs start
dat_NaCl = dat_NaCl%>%
   mutate(sek=(
           as.numeric(as.POSIXct(dat_NaCl$time))-as.numeric(dat_NaCl$time[1], format='%Y-%m-%d %H:%M:%S'))
                )  

dat_NaCl %>%#dplyr arbejder indenfor 'dat' data framen
  mutate(TMP=(p_avg0301+p_avg0302)/2-p_avg0501)%>%#Her regner vi TMP, som dplyr husker nu er en del af den data
  mutate(TMP_slid=rollapply(TMP,100,mean,align="right",fill=NA))%>%#Nu tager vi et glidende gennemsnit
  plot_ly(x=~(sek)/3600,
          y=~p_avg0301,
          name="Pressure before membrane",
          color='#1f77b4',
          type='scatter',
          mode='lines')%>%
  add_lines(y=~p_avg0302,
            name='Pressure after membrane',
            color='#E41317')%>%
  add_lines(y=~TMP_slid,
            name='TMP',
            color='#forestgreen')%>%
  layout(title="NaCl Pressure",
         legend=list(x=0.7,y=0.2),
         yaxis=list(title="Pressure [bar]"),
         xaxis=list(title="Time [h]")) #Her plottet de to tryk på feed siden plus et TMP




```

The conductivity was measured with sensors in the feed and permeate stream. As expected the conductivity in the feed stream increase due to batch setup, and the likewise the conductivity of the permeate stream increase. 
From these measurements the rejection of conductivity was calculated, which decrease from 50 % - 25 % over time as the conductivity increase in the feed stream. 

```{R NaCl plot conductivity, echo=FALSE, message=FALSE}
ay <- list(
  tickfont = list(color = "red"),
  overlaying = "y",
  side = "right",
  title = "Rejection") #Her noget hokus-pokus for at kunne lave 2 y akser


dat_NaCl %>%
  mutate(rejection=(1-(con0501/con0301))*100)%>%
  mutate(feed_slid=rollapplyr(con0301,30,mean,fill=NA))%>%
  mutate(rej_slid=rollapplyr(rejection,30,mean,fill=NA))%>%
  plot_ly(x=~sek/3600,
          y=~feed_slid,
          name="Feed",
          color="red",
          type='scatter',
          mode='lines',
          line=list(color=('#1f77b4')))%>%
  add_trace(y=~con0501,
            name='Permeate',
            line=list(color="#E41317"))%>%
  add_trace(y=~rej_slid,
            name='Rejection',
            yaxis="y2",
            line=list(color="#forestgreen"))%>%
  # Set figure title, x and y-axes titles
  layout(title="NaCl Conductivity",yaxis2=ay,
         legend=list(x=0.6,y=0.5),
         yaxis=list(title="\U03BC S/cm")) #Her conductivity over tid + en form for rejection, 
#læg gerne mærke til farverne der nægter at se


```
IC analysis was made for Sodium and Chloride. The results are presented in the following plot. 
Sodium and Chloride data is presented together where Chloride is represented by circles and sodium represented by Triangles. 
The Concentration measured of feed and concentrate was almost identical for both sodium and chloride, for sodium it cannot be differentiated between feed and concentrate. 
This indicate that there isn't a  major concentration difference across the membrane and it is sufficient to take samples from either the Feed or concentrate stream. 

The plot indicate some increase in concentration for both feed/concentrate and permeate, we do not achieve the increase in concentration that were anticipated, this might be due to a too low water recovery at 88.6 %. 
The final data point for permeate is taken from the well mixed permeate collected during the whole 4 hours, and is therefore lower than the sample taken at 4 hours. 
Likewise the final data point for feed is taken from the feed bucket.  -> hvorfor er den lavere.

```{R NaCl plot IC data, echo=FALSE, message=FALSE}

NaCl_IC_data <- read_excel("data/NaCl_IC_analyse_test.xlsx")
str(NaCl_IC_data)


old_names_IC=colnames(NaCl_IC_data) #Vi finder de latterlige navne kolonnerne i dataen har 
new_names_IC=c("time","Sodium","Chloride","Stream") #Vi finder på nogle lidt bedre nogle
NaCl_IC_data = NaCl_IC_data %>% rename_at(vars(old_names_IC),~new_names_IC) #Vi ændrer navnene til de nye
NaCl_IC_data <- as.data.frame(NaCl_IC_data)

NaCl_Permeate <- filter(NaCl_IC_data, Stream=="Permeate")
NaCl_Feed <- filter(NaCl_IC_data, Stream=="Feed")
NaCl_Concentrate <- filter(NaCl_IC_data, Stream=="Concentrate")   

NaCl_rej_Cl <- (1-(NaCl_Permeate$Chloride[-6]/((NaCl_Feed$Chloride[-1]+NaCl_Concentrate$Chloride)/2)))*100

NaCl_rej_Na <- (1-(NaCl_Permeate$Sodium[-6]/((NaCl_Feed$Sodium[-1]+NaCl_Concentrate$Sodium)/2)))*100


ggplot()+
  geom_point(data=NaCl_IC_data, aes(x=time, y=Chloride, col=Stream), shape= 16)+
  #geom_point(data=NaCl_Feed[-1,], aes(x=NaCl_Feed$time[-1], y=NaCl_rej_Cl))+
  geom_point(data=NaCl_IC_data, aes(x=time, y=Sodium, col=Stream), shape= 17)+
  #geom_point(data=NaCl_Feed[-1,], aes(x=NaCl_Feed$time[-1], y=NaCl_rej_Na))+
  labs(x="Time [h]",y=" concentration [mg/L]")+
  ylim(0,135)+
  ggtitle("Concentration, Dot = Cl, Triangle = Na")


```
```{R NaCl plot temp, include=FALSE, echo=FALSE, message=FALSE}


ggplot()+
  geom_point(data=dat_NaCl, aes(x=time, y=temp0501), shape= 16)+
  labs(x="Time [h]",y=" Temperature")+
  ylim(0,27)+
  ggtitle("temperature")

ggplot()+
  geom_point(data=dat_NaCl, aes(x=time, y=((flow0501/0.053)/(p_avg0301+p_avg0302)/2-p_avg0501)), shape= 16)+
  labs(x="Time [h]",y=" permeability")+
  ylim(0,100)+
  ggtitle("Permeability")

```


```{R NaCl plot bicarbonate, include=FALSE, echo=FALSE, message=FALSE}
#Bicarboante was measured in the feed stream and then in permeate and concentrate at the end of the experiment. 
#It is evident from the following plot that the bicarbonate concentration increase in the feed stream, and is significantly lower in the permeate stream and slightly higher in the concentrate stream. 
B_NaCl_feed <- c(8.4,31,42,43)
tid_kort <- c(0,2,3.5,4)
B_NaCl_permeate <- 15
B_NaCl_concentrate <- 48

SingleSalt_b_NaCl <- data.frame(tid_kort,B_NaCl_feed)
## plot 

ggplot(data=SingleSalt_b_NaCl, aes(x=tid_kort))+
  geom_point(aes( y=B_NaCl_feed, color="Feed"))+
  geom_point(aes(x=4, y=B_NaCl_permeate, color="Permeate"))+
  geom_point(aes(x=4, y=B_NaCl_concentrate, color="Concentrate"))+
  scale_color_manual(values=c("Feed"="red", "Permeate"="blue", "Concentrate"="green"),labels=c("Feed", "Permeate", "Concentrate"))+
  labs(x="Time [h]",y="Bicarbonate  [mg/L]", color="Legend")+
  ggtitle("Bicarbonate concentration NaCl")




```

<h3> CaCl2 3mM </h3>

An experiment with single salt CaCl2 was conducted at concentration 3mM (should have been 1.5 mM). 
The water recovery was 80 %. 
There are further fluctuations in the data which is due to intake of air in the system which lead to the air dampener to be filled with air and thus not dampening the flow fluctuations, thus occurred after 2.5 hours. 

```{R CaCl2 import data plot pressure, echo=FALSE, message=FALSE}
###CaCl2 3 mM 
CWF_CaCl2 = read_delim("data/singlesalt_CaCl2_3mM_15-09-2021.csv",delim = "\t", escape_double = FALSE, 
                  trim_ws = TRUE, skip = 5) #Hente data og få det til passe ned i en tabel
#str(CWF)
dat_CaCl2 = as.data.frame(CWF_CaCl2) #Ændrer strukturen af dataen til noget vi kan arbejde med
old_names=colnames(CWF_CaCl2) #Vi finder de latterlige navne kolonnerne i dataen har 
new_names=c("time","level","con0201","pH0201","con0301","flow0301",
            "p0301","p0302","p0401","flow0401","p0501","con0501",
            "temp0501","p0601","temp0601","16","17","18","19","20",
            "21","pmp0201","pmp0301","pmp0401","pmp0501","flow_avg0301",
            "p_avg0301","p_avg0302","p_avg0401","flow_avg0401",
            "p_avg0501","FT0302","weight0302","flow0501","weight0501","36","pH0301",
            "pH0501","con0302","40") #Vi finder på nogle lidt bedre nogle
dat_CaCl2 = dat_CaCl2 %>% rename_at(vars(old_names),~new_names) #Vi ændrer navnene til de nye
dat_CaCl2$time = dmy_hms(dat_CaCl2$time)#Vi ændrer formatet af 'dato' kolonnen til et standard format for tid og datoer istedet for at det bare er noget tekst
#str(dat)


#tid_sec <- as.numeric(as.POSIXct(dat_CaCl2$time))-as.numeric(as.POSIXct("2021-09-14 11:16:26", #format='%Y-%m-%d %H:%M:%S')) #den regner 2 timer for meget, tag højde for det manuelt checket hvornår flow #rammer 17 ml/min. 
#dat_CaCl2 <- data.frame(dat_CaCl2,tid_sec) #tilføjer tid til data.frame

### Finde t=0 (fosøgsstart = der hvor flow er over 16 mL/min)
flow_boolean = dat_CaCl2$flow0501>16&dat_CaCl2$flow0501<25
start_tid = min(which(flow_boolean))
dat_CaCl2=dat_CaCl2[-c(1:start_tid),]
flow_boolean_slut = dat_CaCl2$flow0501<1
slut_tid = min(which(flow_boolean_slut))
dat_CaCl2=dat_CaCl2[-c(slut_tid:(nrow(dat_CaCl2)) ),]
### Tid i s fra forsøgs start
dat_CaCl2 = dat_CaCl2%>%
   mutate(sek=(
           as.numeric(as.POSIXct(dat_CaCl2$time))-as.numeric(dat_CaCl2$time[1], format='%Y-%m-%d %H:%M:%S'))
                )  

dat_CaCl2 %>%#dplyr arbejder indenfor 'dat' data framen
  mutate(TMP=(p_avg0301+p_avg0302)/2-p_avg0501)%>%#Her regner vi TMP, som dplyr husker nu er en del af den data
  mutate(TMP_slid=rollapply(TMP,100,mean,align="right",fill=NA))%>%#Nu tager vi et glidende gennemsnit
  plot_ly(x=~sek/3600,
          y=~p_avg0301,
          name="Pressure before membrane",
          color='#1f77b4',
          type='scatter',
          mode='lines')%>%
  add_lines(y=~p_avg0302,
            name='Pressure after membrane',
            color='#E41317')%>%
  add_lines(y=~TMP_slid,
            name='TMP',
            color='#forestgreen')%>%
  layout(title="CaCl2 Pressure",
         legend=list(x=0.7,y=0.2),
         yaxis=list(title="Pressure [bar]", range=c(0,3.5)),
         xaxis=list(title="Time [h]", range=c(0,4)))#Her plottet de to tryk på feed siden plus et TMP


``` 

This intake of air into the system also had an effect on conductivity and conductivity rejection as there are major fluctuations, also the rejection increase after these flucturations are introduced, this is different from the NaCl experiment. . 
Otherwise similar trends as from the NaCl as seen in conductivty, conductivity rejection is about 60-50 % which is significantly higher than for the NaCl experiment. The increase in conductivity rejection might be due to presence of multicalent ions. 


```{R CaCl2 plot conductivity, echo=FALSE, message=FALSE}
ay <- list(
  tickfont = list(color = "red"),
  overlaying = "y",
  side = "right",
  title = "Rejection") #Her noget hokus-pokus for at kunne lave 2 y akser


dat_CaCl2 %>%
  mutate(rejection=(1-(con0501/con0301))*100)%>%
  mutate(feed_slid=rollapplyr(con0301,30,mean,fill=NA))%>%
  mutate(rej_slid=rollapplyr(rejection,30,mean,fill=NA))%>%
  plot_ly(x=~sek/3600,
          y=~feed_slid,
          name="Feed",
          color="red",
          type='scatter',
          mode='lines',
          line=list(color=('#1f77b4')))%>%
  add_trace(y=~con0501,
            name='Permeate',
            line=list(color="#E41317"))%>%
  add_trace(y=~rej_slid,
            name='Rejection',
            yaxis="y2",
            line=list(color="#forestgreen"))%>%
  # Set figure title, x and y-axes titles
  layout(title="CaCl2 Conductivity",yaxis2=ay,
         legend=list(x=0.6,y=0.5),
         yaxis=list(title="\U03BC S/cm"),
         xaxis=list(title="Time [h]")) #Her conductivity over tid + en form for rejection, 
#læg gerne mærke til farverne der nægter at se


```
IC analysis was made for Calcium and Chloride. The results are presented in the following plot where Chloride is presented by circles and Calcium presented by triangles. 
As for the NaCl experiment there was almost identical concentration for feed and concentrate for both Chloride and Calcium, which back the previous conclusion of taking fewer samples. 

There is a higher concentration of Chloride in this expeirment compared to the NaCl experiment, otherwise there is similar trend in the plot, with increase in concentraiton of both feed/concentrate and permeate.

```{R CaCl2 plot IC data, echo=FALSE, message=FALSE}

CaCl2_IC_data <- read_excel("data/NaCl_IC_analyse_test.xlsx",2)
str(CaCl2_IC_data)


old_names_IC_CaCl2=colnames(CaCl2_IC_data) #Vi finder de latterlige navne kolonnerne i dataen har 
new_names_IC_CaCl2=c("time","Calcium","Chloride","Stream") #Vi finder på nogle lidt bedre nogle
CaCl2_IC_data = CaCl2_IC_data %>% rename_at(vars(old_names_IC_CaCl2),~new_names_IC_CaCl2) #Vi ændrer navnene til de nye
CaCl2_IC_data <- as.data.frame(CaCl2_IC_data)

CaCl2_Permeate <- filter(CaCl2_IC_data, Stream=="Permeate")
CaCl2_Feed <- filter(CaCl2_IC_data, Stream=="Feed")
CaCl2_Concentrate <- filter(CaCl2_IC_data, Stream=="Concentrate")   

CaCl2_rej_Cl <- (1-(CaCl2_Permeate$Chloride[-6]/((CaCl2_Feed$Chloride[-1]+CaCl2_Concentrate$Chloride)/2)))*100

CaCl2_rej_Ca <- (1-(CaCl2_Permeate$Calcium[-6]/((CaCl2_Feed$Calcium[-1]+CaCl2_Concentrate$Calcium)/2)))*100


ggplot()+
  geom_point(data=CaCl2_IC_data, aes(x=time, y=Chloride, col=Stream), shape= 16)+
  #geom_point(data=CaCl2_Feed[-1,], aes(x=CaCl2_Feed$time[-1], y=CaCl2_rej_Cl))+
  geom_point(data=CaCl2_IC_data, aes(x=time, y=Calcium, col=Stream), shape= 17)+
  #geom_point(data=CaCl2_Feed[-1,], aes(x=CaCl2_Feed$time[-1], y=CaCl2_rej_Ca))+
  labs(x="Time [h]",y=" Concentration [mg/L]")+
  ylim(0,350)+
  ggtitle(" Concentration, Dot = Cl, Triangle = Ca")
  

       
```







<h3> Na2OSiO2 3mM </h3>

An experiment with single salt Na2OSiO2 was conducted at concentration 1mM. 
The water recovery was ?? %. 
Again the large flucturations is due to sampleing of the permeate stream. 

```{R Na2OSiO2 import data plot pressure, echo=FALSE, message=FALSE}
###Na2OSiO2 1 mM 
CWF <- read_delim("data/singlesalt_Na2OSiO2_1mM_22-09-2021.csv", 
                    delim = "\t", escape_double = FALSE, 
                    trim_ws = TRUE, skip = 5) #Hente data og få det til passe ned i en tabel
#str(CWF)
dat_SiO2 = as.data.frame(CWF) #Ændrer strukturen af dataen til noget vi kan arbejde med
old_names=colnames(CWF) #Vi finder de latterlige navne kolonnerne i dataen har 
new_names=c("time","level","con0201","pH0201","con0301","flow0301",
            "p0301","p0302","p0401","flow0401","p0501","con0501",
            "temp0501","p0601","temp0601","16","17","18","19","20",
            "21","pmp0201","pmp0301","pmp0401","pmp0501","flow_avg0301",
            "p_avg0301","p_avg0302","p_avg0401","flow_avg0401",
            "p_avg0501","FT0302","weight0302","flow0501","weight0501","36","pH0301",
            "pH0501","con0302","40") #Vi finder på nogle lidt bedre nogle
dat_SiO2 = dat_SiO2 %>% rename_at(vars(old_names),~new_names) #Vi ændrer navnene til de nye
dat_SiO2$time = dmy_hms(dat_SiO2$time)#Vi ændrer formatet af 'dato' kolonnen til et standard format for tid og datoer istedet for at det bare er noget tekst


### Finde t=0 (fosøgsstart = der hvor flow er over 16 mL/min)
flow_boolean_SiO2 = dat_SiO2$flow0501>16&dat_SiO2$flow0501<25
start_tid_SiO2 = min(which(flow_boolean_SiO2))
dat_SiO2=dat_SiO2[-c(1:start_tid_SiO2),]
flow_boolean_slut_SiO2 = dat_SiO2$flow0501<5
slut_tid_SiO2 = min(which(flow_boolean_slut_SiO2))
dat_SiO2=dat_SiO2[-c(slut_tid_SiO2:(nrow(dat_SiO2)) ),]
### Tid i s fra forsøgs start
dat_SiO2 = dat_SiO2%>%
   mutate(sek=(
           as.numeric(as.POSIXct(dat_SiO2$time))-as.numeric(dat_SiO2$time[1], format='%Y-%m-%d %H:%M:%S'))
                )  

dat_SiO2 %>%#dplyr arbejder indenfor 'dat' data framen
  mutate(TMP=(p_avg0301+p_avg0302)/2-p_avg0501)%>%#Her regner vi TMP, som dplyr husker nu er en del af den data
  mutate(TMP_slid=rollapply(TMP,100,mean,align="right",fill=NA))%>%#Nu tager vi et glidende gennemsnit
  plot_ly(x=~sek/3600,
          y=~p_avg0301,
          name="Pressure before membrane",
          color='#1f77b4',
          type='scatter',
          mode='lines')%>%
  add_lines(y=~p_avg0302,
            name='Pressure after membrane',
            color='#E41317')%>%
  add_lines(y=~TMP_slid,
            name='TMP',
            color='#forestgreen')%>%
  layout(title="SiO2 Pressure",
         legend=list(x=0.7,y=0.2),
         yaxis=list(title="Pressure [bar]", range=c(0,3.5)),
         xaxis=list(title="Time [h]", range=c(0,4)))#Her plottet de to tryk på feed siden plus et TMP

```
The same trends as for the NaCl and the CaCl2 experiments are seen in the SiO2 expeirment regarding conductivity rejection. Where conductivity rejection is about 70-60 %.   
There are some fluctuations in just after 2 and 3 hours, this might be due to the large flucturations due to sampling of permeate also seen in the previous plot. 

```{R Na2OSiO2 plot conductivity, echo=FALSE, message=FALSE}

ay <- list(
  tickfont = list(color = "red"),
  overlaying = "y",
  side = "right",
  title = "Rejection") #Her noget hokus-pokus for at kunne lave 2 y akser


dat_SiO2 %>%
  mutate(rejection=(1-(con0501/con0301))*100)%>%
  mutate(feed_slid=rollapplyr(con0301,30,mean,fill=NA))%>%
  mutate(rej_slid=rollapplyr(rejection,30,mean,fill=NA))%>%
  plot_ly(x=~sek/3600,
          y=~feed_slid,
          name="Feed",
          color="red",
          type='scatter',
          mode='lines',
          line=list(color=('#1f77b4')))%>%
  add_trace(y=~con0501,
            name='Permeate',
            line=list(color="#E41317"))%>%
  add_trace(y=~rej_slid,
            name='Rejection',
            yaxis="y2",
            line=list(color="#forestgreen"))%>%
  # Set figure title, x and y-axes titles
  layout(title="SiO2 Conductivity",yaxis2=ay,
         legend=list(x=0.6,y=0.5),
         yaxis=list(title="\U03BC S/cm"),
         xaxis=list(title="Time [h]")) #Her conductivity over tid + en form for rejection, 
#læg gerne mærke til farverne der nægter at se


```

The concentration of SiO2 was measured with Hack kits, and the concentration of Na was measured with IC analysis, similar to the NaCl and the CaCl2 experiments. 
Also for this experiment there is not a large difference between concentrate (red) and feed (red), which again confirmed that only one sample is necessary. 
For SiO2presented by dots, there is not a huge difference between feed/concentrate and permeate, indicating a low rejection.This also means that there is not a major increase in concentration of the feed, it is almost constant with some flucturations, which also could be caused by uncertainy of the measureing analysis which is +/- XX mg/L. 

For Na there is a larger difference between feed/concenrate and permeate and also increase in both over the duration of the experiment. The data for Na is more similar to the results seen for the two other experiemtn with NaCl and CaCl2. 


```{R Na2OSiO2 plot IC analyse, echo=FALSE, message=FALSE}
 #Na2OSiO2 data 

SiO2_IC_data <- read_excel("data/NaCl_IC_analyse_test.xlsx",3)
str(SiO2_IC_data)


old_names_IC_SiO2=colnames(SiO2_IC_data) #Vi finder de latterlige navne kolonnerne i dataen har 
new_names_IC_SiO2=c("time","Silica","Sodium","Stream") #Vi finder på nogle lidt bedre nogle
SiO2_IC_data = SiO2_IC_data %>% rename_at(vars(old_names_IC_SiO2),~new_names_IC_SiO2) #Vi ændrer navnene til de nye
SiO2_IC_data <- as.data.frame(SiO2_IC_data)

SiO2_Permeate <- filter(SiO2_IC_data, Stream=="Permeate")
SiO2_Feed <- filter(SiO2_IC_data, Stream=="Feed")
SiO2_Concentrate <- filter(SiO2_IC_data, Stream=="Concentrate")   

SiO2_rej_Si<- (1-(SiO2_Permeate$Silica[-6]/((SiO2_Feed$Silica[-1]+SiO2_Concentrate$Silica)/2)))*100

SiO2_rej_Na <- (1-(SiO2_Permeate$Sodium[-6]/((SiO2_Feed$Sodium[-1]+SiO2_Concentrate$Sodium)/2)))*100


ggplot()+
  geom_point(data=SiO2_IC_data, aes(x=time, y=Silica, col=Stream), shape= 16)+
  #geom_point(data=SiO2_Feed[-1,], aes(x=SiO2_Feed$time[-1], y=SiO2_rej_Cl))+
  geom_point(data=SiO2_IC_data, aes(x=time, y=Sodium, col=Stream), shape= 17)+
  #geom_point(data=SiO2_Feed[-1,], aes(x=SiO2_Feed$time[-1], y=SiO2_rej_Ca))+
  labs(x="Time [h]",y=" Concentration [mg/L]")+
  ggtitle("Concentration,  Dot = SiO2, Triangle = Na")

```
  
```{R Na2OSiO2 old plot, include=FALSE, echo=FALSE, message=FALSE}
#old måde at plotte på. 
tid <- c(1,2,3,3.5,4)
#concentrations data: 
SiO2_conc_feed <- c(60.7,60.3,63.6,63.6,63)
SiO2_conc_conc <- c(62,62.7,63.9,63.4,65.3)
SiO2_conc_permeate <- c(52.8,55.5,54.7,56.7,51.6)
SiO2_conc_inlet = (SiO2_conc_feed+SiO2_conc_conc)/2
SiO2_rejection = (1-(SiO2_conc_permeate/SiO2_conc_feed))*100

###pH data: 
SiO2_ph_feed <- c(8.29,8.26,8.29,8.35,8.37)
SiO2_ph_conc <- c(8.29,8.27,8.29,8.33,8.37)
SiO2_ph_permeate <- c(7.77,7.87,7.93,7.96,7.9)
SiO2_ph_inlet = (SiO2_ph_feed+SiO2_ph_conc)/2

SiO2 <- data.frame(tid,SiO2_conc_feed,SiO2_conc_conc, SiO2_conc_permeate,SiO2_ph_feed,SiO2_ph_conc, SiO2_ph_permeate)


ggplot(data=SiO2, aes(x=tid))+
  geom_point(aes( y=SiO2_conc_feed, color="Feed"),shape= 16)+
  geom_point(aes( y=SiO2_conc_conc,color="Concentrate"),shape= 16)+
  geom_point(aes( y=SiO2_conc_permeate,color="Permeate"),shape= 16)+
   scale_color_manual(values=c("Feed"="green","Concentrate"="red","Permeate"="blue"),labels=c("Feed", "Concentrate", "Permeate"))+
  labs(x="Time[h]",y="SiO2 concentration  [mg/L]", color="Legend")+
  ggtitle("Concentration, feed, concentrate, permeate")




```

<h3> Rejection IC data </h3>

The rejection of the 3 singlesalt experiments are compared in the follow plot. 
The rejection in the CaCl2 experiment is significantly larger, as well as Sodium fro Na2OSiO2 experiment. The rejection from CaCl2 increase slightly over the course of the experiment, where it was expected that the rejection would decrease as seen for the conductivity rejection, this might be due to the small no of data samples for IC data. The rejection is about 50-60% which is similar for the conductivity experiment. 

The rejection in the NaCl experiment is significantly lower than the CaCl2 experiment, and is more constant over the 4 hours. When comparing to the conductivity rejection which decrease from 50-25 % it is similar. 
The rejection of SiO2 (from the Na2OSiO2) is lower than both the rejection seen in the NaCl and CaCl2 experiment. The rejection of SiO2 is fluctuating around 13 %. The Sodium concentraiton is higher above 50 % which better match the conductivity rejection at 60-70%, Sodium thus must account the conductivity in this experiment.   

It is interesting to compare the chloride rejection from the two experiment where there is a higher concentration in the CaCl2 (double) but also significantly higher rejection around double. 
It would be expected to have similar or lower rejection with increase in concentration therefore the increase in rejection for the CaCl2 experiment is most likely due to the presence of multivalent ions. 
There is a much higher rejection of Calcium than sodium, despite a similar concentration of 3mM, this difference is again contributed to the nature of the multivalent calcium ions. 

-> mere teroi om hvorfor de har bedre rejection. 



```{r Summary rejection, echo=FALSE, message=FALSE}
#ggplot(data=SiO2, aes(x=tid))+
#  geom_point(aes(y=SiO2_rejection),color="black")+
#  ylim(0,100)+
#  ggtitle("Rejection %")

ggplot()+
  geom_point(data=CaCl2_Feed[-1,], aes(x=CaCl2_Feed$time[-1], y=CaCl2_rej_Ca, color="CaCl2 R Ca"))+
  geom_point(data=CaCl2_Feed[-1,], aes(x=CaCl2_Feed$time[-1], y=CaCl2_rej_Cl,color="CaCl2 R Cl"))+
  geom_point(data=NaCl_Feed[-1,], aes(x=NaCl_Feed$time[-1], y=NaCl_rej_Na,color="NaCl R Na"))+
  geom_point(data=NaCl_Feed[-1,], aes(x=NaCl_Feed$time[-1], y=NaCl_rej_Cl,color="NaCl R Cl"))+
  geom_point(data=SiO2_Feed[-1,], aes(x=SiO2_Feed$time[-1], y=SiO2_rej_Na,color="SiO2 R Na"))+
  geom_point(data=SiO2_Feed[-1,], aes(x=SiO2_Feed$time[-1], y=SiO2_rej_Si,color="SiO2 R SiO2"))+
  scale_color_manual(values=c("CaCl2 R Ca"="red", "CaCl2 R Cl"="blue", "NaCl R Na"="green", "NaCl R Cl"="orange", "SiO2 R Na"="black", "SiO2 R SiO2"="purple"),labels=c("CaCl2 R Ca", "CaCl2 R Cl", "NaCl R Na", "NaCl R Cl", "SiO2 R Na", "SiO2 R Si"))+
  labs(x="Time [h]",y="Rejection  %", color="Legend")+
  ylim(0,100)+
  ggtitle("Rejection Singlesalt")

mean_CaCl2_rej_Ca <- mean(CaCl2_rej_Ca)
mean_CaCl2_rej_Cl <- mean(CaCl2_rej_Cl)
mean_NaCl_rej_Na <- mean(NaCl_rej_Na)
mean_NaCl_rej_Cl <- mean(NaCl_rej_Cl)
mean_SiO2_rej_Na <- mean(SiO2_rej_Na)
mean_SiO2_rej_Si <- mean(SiO2_rej_Si)

rejection_data <- data.frame(
  ion=c("CaCl2_Ca", "CaCl2_Cl","NaCl_Na", "NaCl_Cl","SiO2_Na", "SiO2_Si" ), 
  rej=c(mean_CaCl2_rej_Ca, mean_CaCl2_rej_Cl, mean_NaCl_rej_Na, mean_NaCl_rej_Cl, mean_SiO2_rej_Na, mean_SiO2_rej_Si))


ggplot(data=rejection_data, aes(x=ion, y=rej))+
  geom_bar(stat="identity")+
  geom_text(aes(label=scales::percent(rej/100,accuracy = 0.1)),vjust=-0.3, size=3.5)+
  ylim(0,100)+labs(y="Rejection  %", x="Species")


rejection_data[1:2,]
```

<h3> Bicarboante </h3>
Bicarboante was measured in the feed stream and then in permeate and concentrate at the end of the experiment. 
When comparing the different experiment there is singiciantly higher concentaiton of bicarbonate in SiO2 expeirment, floweed by NaCl and CaCl2 which have more similar bicarbonate concentraiton. 
There is a general trend for all experiments, that the bicarbonate concentration increase in the feed stream, and is significantly lower in the permeate stream and slightly higher in the concentrate stream. 

```{r Summary bicarbonat, echo=FALSE, message=FALSE}


B_NaCl <- c(8.4,31,42,43,15,48)
B_CaCl2 <- c(6,15,18,20,7.8,20)

B_Na2OSiO2 <- c(126,128,141,157,196,205,61,212)
tid_lang <- (c(0,0,1,2,3.5,4,4,4))
tid_kort <- c(0,2,3.5,4,4,4)

SingleSalt_Cl <- data.frame(tid_kort,B_NaCl, B_CaCl2)
Singlesalt_SiO2 <- data.frame(tid_lang,B_Na2OSiO2)


### Plottet sammen ###

ggplot(data=SingleSalt_Cl, aes(x=tid_kort))+
  geom_point(aes( y=B_NaCl, color="NaCl"))+
  geom_point(aes( y=B_CaCl2,color="CaCl2"))+
  geom_point(data=Singlesalt_SiO2, aes(x=tid_lang, y=B_Na2OSiO2, color="SiO2"))+
  scale_color_manual(values=c("NaCl"="red","CaCl2"="green", "SiO2"="blue"),labels=c("NaCl", "CaCl2", "SiO2"))+
  labs(x="Time [h]",y="Bicarbonate  [mg/L]", color="Legend")+
  ggtitle("Bicarbonate concentration Singlesalt")
```


<h3> pH sammenligning </h3>

The pH between each experiment vary greatly despite the pH being set at 8.5. 
The only pH which remained at pH 8.5 was for the Na2OSiO2 experiment, which increased slightly but otherwise was stable during the experiment. 
For the NaCl experiment the pH had already increased to pH 8.1 at the start of the experiment and the pH decreased during the filtration, to about pH 7.7. 
The CaCl2 experiment had the lowest pH at 7.3 initally and decrease to 7.4 with flucturations which might be caused by the inlet of air described earlier arond 2.5 hours. 
The pH is not stable for the salt solutions produced from the pH is set to the experiment is started, this pose a problem in relation to relatability to authentic CT water. 




```{r Summary pH, echo=FALSE, message=FALSE}

ggplot()+
  geom_line(data=dat_NaCl, aes(x=sek/3600, y=pH0201, color="NaCl"))+
  geom_line(data=dat_CaCl2, aes(x=sek/3600, y=pH0201,color="CaCl2"))+
  geom_line(data=dat_SiO2, aes(x=sek/3600, y=pH0201,color="SiO2"))+
  scale_color_manual(values=c("NaCl"="red","CaCl2"="green", "SiO2"="blue"),labels=c("NaCl", "CaCl2", "SiO2"))+
  labs(x="Time [h]",y="pH", color="Legend")+
  ggtitle("pH Singlesalt")


```


