---
title: "SPRR Regressions"
author: "Steffen"
date: "12/5/2022"
output: 
  html_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#Loading af pakker 
library(plyr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(visdat)
library(GGally)
library(Hmisc)
library(DMwR2)
library(data.table)
library(mltools)
library(ggfortify)
library(ggiraphExtra)
library(coronavirus)
library(lubridate)
library(plotly)
#library(naniar)
library(readxl)
require(readr)
library(zoo)
library(latex2exp)
library(fs)
library(plyr)
library(matrixStats)
library(haven)
library(sjmisc)
require(gridExtra)
require(ggpubr)
library(reshape2)


colors = c(
    '#1f77b4',  # muted blue
    '#ff7f0e',  # safety orange
    '#2ca02c',  # cooked asparagus green
    '#d62728',  # brick red
    '#9467bd',  # muted purple
    '#8c564b',  # chestnut brown
    '#e377c2',  # raspberry yogurt pink
    '#7f7f7f',  # middle gray
    '#bcbd22',  # curry yellow-green
    '#17becf'   # blue-teal
)

```

# Steady State Databehandling  {.tabset}



```{r import en masse data, include=FALSE}
Ion_data_frame = data.frame()
## SPRR data håndtering
SPRR = read.table(file='data/SPRR_df.csv', header = T,sep = "\t",stringsAsFactors = T)
SPRR_pH= c(NA,9.37,9.26,NA,9.26,9.35,NA,9.67,9.68,NA,9.56,9.66,NA,9.83,9.89,NA,9.81,9.87)
SPRR_con= c(NA,2350,1670,NA,2330,1680,NA,2440,1750,NA,2510,1760,NA,2450,1840,NA,2540,1830)
#SPRR_type=rep(c("SPRR"),each=18)
SPRR_names = c("SPRR_1","SPRR_2","SPRR_3","SPRR_4","SPRR_5","SPRR_6","SPRR_7","SPRR_8","SPRR_9","SPRR_10","SPRR_11","SPRR_12","SPRR_13","SPRR_14","SPRR_15","SPRR_16","SPRR_17","SPRR_18")


SPRR_wrangle = cbind(SPRR%>%filter(Stream == "Feed"),SPRR%>%filter(Stream == "Rejection")%>%select("Na","Ca","Cl","SO4","SiO2","HCO3"))
SPRR_wrangle$pH = SPRR_pH
SPRR_wrangle$con = SPRR_con
#SPRR_wrangle$type = SPRR_type


colnames(SPRR_wrangle) = c("name","Stream","Cl_ratio","SiO2_teo","pH","Ca","Na","Cl","SO4","SiO2_mgL","HCO3","Rej_Na","Rej_Ca","Rej_Cl","Rej_SO4","Rej_SiO2","Rej_HCO3","Conductivity")
SPRR_wrangle$name = SPRR_names
SPRR_clean = SPRR_wrangle%>%select(-c("Stream","SiO2_teo","HCO3","Rej_HCO3","Cl_ratio"))
SPRR_clean$state = "Steady State"
SPRR_clean$type = "SPRR"
SPRR_clean$pH[1]=9.33
SPRR_clean$time=NA
SPRR_clean$start_vol = NA

###multisalt håndtering
M_9.2 = read.table(file='data/M9.2_df.csv', header = T,sep = "\t",stringsAsFactors = T)
M_9.2_clean = M_9.2%>%select(-c("time","conductivity"))
M_9.2_clean$Conductivity = c(1560,1730,1880,2080,2390,2700)
M_9.2_clean$state = "Batch"
M_9.2_clean$type = "M_9.2"
M_9.2_clean$name = c("M_9.2_3.5h","M_9.2_5h","M_9.2_6h","M_9.2_7h","M_9.2_8h","M_9.2_8.7h")
M_9.2_clean$time = c(3.5,5,6,7,8,8.7)
M_9.2_clean$start_vol = 10

M_10 = read.table(file='data/M10_df.csv', header = T,sep = "\t",stringsAsFactors = T)
M_10_clean = M_10%>%select(-c("time"))
M_10_clean$Conductivity = c(1830,2050,2350,2550,2830,3250)
M_10_clean$state = "Batch"
M_10_clean$type = "M_10"
M_10_clean$pH = c(10.13,10.15,10.17,10.19,10.21,10.24)
M_10_clean$name = c("M_10_3h","M_10_4h","M_10_5h","M_10_5.5h","M_10_6h","M_10_6.5h")
M_10_clean$time = c(3,4,5,5.5,6,6.5)
M_10_clean$start_vol = 8.5

M_10.5 = read.table(file='data/M10.5_df.csv', header = T,sep = "\t",stringsAsFactors = T)
M_10.5_clean = M_10.5%>%select(-c("time"))
M_10.5_clean$Conductivity = c(2080,2390,2660,3020,3570,4470)
M_10.5_clean$state = "Batch"
M_10.5_clean$type = "M_10.5"
M_10.5_clean$pH = c(10.5,10.52,10.54,10.56,10.59,10.63)
M_10.5_clean$name = c("M_10.5_2.5h","M_10.5_4h","M_10.5_5h","M_10.5_6h","M_10.7h","M_10.5_8h")
M_10.5_clean$time = c(2.5,4,5.5,6,7,8)
M_10.5_clean$start_vol = 10

### ICR data
ICR_1 = read.table(file='data/ICR_df.csv', header = T,sep = "\t",stringsAsFactors = T)
colnames(ICR_1) = c("name","SiO2_mgL","Na","Cl","SO4","Ca","pH","Rej_Cl","Rej_SO4","Rej_Na","Rej_Ca","Rej_SiO2","state")
ICR_clean = ICR_1
ICR_clean$Conductivity = c(2477,2517,2570,2625,2685,2740,2810,2881,2951,3040,3126,3221,3376,3568,4019)
SPRR_clean$Conductivity[1]=4210
ICR_clean$type = "ICR"
ICR_clean$time = c(20/60,40/60,60/60,80/60,100/60,2,140/60,160/60,3,200/60,220/60,240/60,270/60,300/60,360/60)
ICR_clean$start_vol = 10

###Sættes sammen
col_order <- c("name","Na","Cl","SO4","Ca","SiO2_mgL","pH","Rej_Cl","Rej_SO4","Rej_Na","Rej_Ca","Rej_SiO2","state","type","time","start_vol")
M_9.2_clean = M_9.2_clean[,col_order]
M_10_clean = M_10_clean[,col_order]
M_10.5_clean = M_10.5_clean[,col_order]
SPRR_clean = SPRR_clean[,col_order]
ICR_clean = ICR_clean[,col_order]

Ion_data_frame = rbind(M_9.2_clean,M_10_clean,M_10.5_clean,SPRR_clean,ICR_clean)
Ion_data_frame[1:18,8:12] = Ion_data_frame[1:18,8:12]*100
Mw_Cl=35.45
Mw_Na=22.99
Mw_Ca=40.078
Mw_SO4=96.06
Mw_SiO2=60.08
Ion_data_frame = Ion_data_frame%>%mutate("Na_mmol"=Na/Mw_Na)
Ion_data_frame = Ion_data_frame%>%mutate("Ca_mmol"=Ca/Mw_Ca)
Ion_data_frame = Ion_data_frame%>%mutate("Cl_mmol"=Cl/Mw_Cl)
Ion_data_frame = Ion_data_frame%>%mutate("SO4_mmol"=SO4/Mw_SO4)
Ion_data_frame = Ion_data_frame%>%mutate("SiO2_mmol"=SiO2_mgL/Mw_SiO2)


### noget med recovery
Ion_data_frame = Ion_data_frame%>%mutate("perm_vol"=time*1.02)
Ion_data_frame = Ion_data_frame%>%mutate("Recovery"=100*(1-(start_vol-perm_vol)/start_vol))
Ion_data_frame=Ion_data_frame[19:36,]


#Udtryk for ladning af silica som funk af pH, jeg kan ikkehuske hvor det kommer fra
a=1.00016
b=2.314233
c=9.831689
Ion_data_frame = Ion_data_frame%>%mutate(SiO2_ladet =  a/(1+exp(-b*(pH-c))))
#Ion_data_frame = Ion_data_frame%>%mutate(SiO2_ladet1=-0.0052*pH^5+0.2074*pH^4-3.2404*pH^3+24.84*pH^2-93.425*pH+137.74) #Gammelt udtryk for samme




Ion_data_frame = Ion_data_frame%>%mutate(Cl_SO4 = Cl_mmol/(Cl_mmol+SO4_mmol))
Ion_data_frame = Ion_data_frame%>%mutate(total_sio2_ladet=SiO2_mmol*SiO2_ladet)
Ion_data_frame = Ion_data_frame%>%mutate(anion_total = total_sio2_ladet+SO4_mmol+Cl_mmol)
Ion_data_frame = Ion_data_frame%>%mutate(Cl_anion = Cl_mmol/anion_total)
Ion_data_frame=Ion_data_frame[!is.na(Ion_data_frame$Na),]

Ion_data_frame_both=Ion_data_frame%>%filter(name!="SPRR_1")%>%filter(name!="SPRR_8")
Ion_data_frame=Ion_data_frame_both

```

# Silica Rejection  {.tabset}

## 2D Multiple Linear Regression
We assume that pH is the major variable that controls silica rejection.
A liniear regression between the two shows correlation to some degree.
```{r Silica rej , echo=FALSE}


#Funktion der laver plots af ens model:
ggplotRegression <- function (fit) {

require(ggplot2)

ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}

#### ONE VARIABLE ####
##SiO2 Rejection mod pH ##
fit_SiO2_pH = lm(Rej_SiO2~pH, data = Ion_data_frame)
ggplotRegression(fit_SiO2_pH)+ylab("SiO2 Rejection [%]")
summary(fit_SiO2_pH)
#plot(fit_SiO2_pH)



## noget med nogle Residuals
cooksD <- cooks.distance(fit_SiO2_pH)
influential <- cooksD[(cooksD > (3 * mean(cooksD, na.rm = TRUE)))]
influential
#Number 23 (SPRR 5) has cooks distance >3x avg, if we exclude it our model is now:

fit_SiO2_pH_cook = lm(Rej_SiO2~pH, data = Ion_data_frame%>%filter(name!="SPRR_5"))
ggplotRegression(fit_SiO2_pH_cook)+ylab("SiO2 Rejection [%]")
#plot(fit_SiO2_pH_cook)
#Which is a slightly better fit R2=0.87 vs 0.83. Can you just do that? who knows?

##SiO2 Rejection mod Cl/SO4##
fit_SiO2_Cl_SO4= lm(Rej_SiO2~Cl_SO4, data = Ion_data_frame)
ggplotRegression(fit_SiO2_Cl_SO4)+ylab("SiO2 Rejection [%]")
summary(fit_SiO2_Cl_SO4)


##SiO2 Rejection mod [SiO2]##
fit_SiO2_sio2 = lm(Rej_SiO2~SiO2_mmol, data = Ion_data_frame)
ggplotRegression(fit_SiO2_sio2)+ylab("SiO2 Rejection [%]")
summary(fit_SiO2_sio2)

#### TWO VARIABLES ####
fit_SiO2_pH_sio2 = lm(Rej_SiO2~pH+SiO2_mmol, data = Ion_data_frame)
ggplotRegression(fit_SiO2_pH_sio2)+ylab("SiO2 Rejection [%]")
#plot(fit_SiO2_pH2)
summary(fit_SiO2_pH_sio2)

plot(x=predict(fit_SiO2_pH), y=na.omit(Ion_data_frame$Rej_SiO2),
     xlab='Predicted Values',
     ylab='Actual Values',
     main='pH',
     abline(a=0, b=1))

plot(x=predict(fit_SiO2_pH_sio2), y=na.omit(Ion_data_frame$Rej_SiO2),
     xlab='Predicted Values',
     ylab='Actual Values',
     main='pH and SiO2 Concentration',
     abline(a=0, b=1))


y1=predict(fit_SiO2_pH)
y2=predict(fit_SiO2_pH_sio2)
x=na.omit(Ion_data_frame$Rej_SiO2)
Silica_models=data.frame(x,y1,y2)
colnames(Silica_models)=c("Actual","pH model","pH+[SiO2] model")
Silica_models=Silica_models%>%gather(key="key",value="value","pH model","pH+[SiO2] model")
ggplot(Silica_models,aes(x=Actual,y=value,color=key))+geom_point()+geom_abline()
#Ion_data_frame = Ion_data_frame%>%mutate(SiO2_ladet=((fit_SiO2_pH$coef)[2]*pH+(fit_SiO2_pH$coef)[1])/100*SiO2_mmol) #regn ladning fraction ud fra rejection?? we don't do this


### Rejection mod pH og Cl/anion
fit_SiO2_pH_cl_anion = lm(Rej_SiO2~pH+Cl_anion, data = Ion_data_frame)
#ggplotRegression(fit_SiO2_pH_cl_anion)+ylab("SiO2 Rejection [%]")
summary(fit_SiO2_pH_cl_anion)

#### MULTIVARIATE ####

### Rejection mod pH og Cl/anion og [sio2]
fit_SiO2_pH_Cl_SO4_sio2 = lm(Rej_SiO2~pH+Cl_SO4+SiO2_mmol, data = Ion_data_frame)
#ggplotRegression(fit_SiO2_pH_Cl_SO4_sio2)+ylab("SiO2 Rejection [%]")
summary(fit_SiO2_pH_Cl_SO4_sio2)
```
Conclusion: Silica rejection can be predicted from pH and concentration of silica on these samples.

## 3D Representation
### Silica as function of pH and silica concentration
```{R 3D Silica_pH_SiO2mmol, echo=FALSE, message=FALSE, warning=FALSE, , echo=FALSE}

#SPRR_rejection <- na.omit((SPRR_data%>%filter(Stream == "Rejection")))

library(reshape2)

Ion_data_frame=Ion_data_frame[!is.na(Ion_data_frame$Na),]



#Vores linear model:
Rejection_lm <- lm(Rej_SiO2 ~ pH + SiO2_mmol,data=Ion_data_frame)
#Graph Resolution (more important for more complex shapes)
graph_reso <- 0.05

#Setup Axis
axis_x <- seq(min(Ion_data_frame$pH), max(Ion_data_frame$pH), by = graph_reso)
axis_y <- seq(min(Ion_data_frame$SiO2_mmol), max(Ion_data_frame$SiO2_mmol), by = graph_reso)

#Sample points
Rejection_lm_surface <- expand.grid(pH = axis_x,SiO2_mmol = axis_y,KEEP.OUT.ATTRS = F)
Rejection_lm_surface$Rej_SiO2 <- predict.lm(Rejection_lm, newdata = Rejection_lm_surface)
Rejection_lm_surface <- acast(Rejection_lm_surface, SiO2_mmol ~ pH, value.var = "Rej_SiO2") #y ~ x

axx <- list(
  title = "pH")
axy <- list(
  title = "SiO<sub>2</sub> Concentration [mM]")
axz <- list(
  title = "SiO<sub>2</sub> Rejection [%]")

R_plot <- plot_ly(
 Ion_data_frame,
  x = ~ pH,
  y = ~ SiO2_mmol,
  z = ~ Rej_SiO2,
  type = "scatter3d",
  mode = "markers",
  marker = list(
    color = ~ Rej_SiO2,
    colorscale = 'magma',
    line = list(
        color = 'rgb(0, 0, 0)',
        width = 1
    )
    )
)%>%layout(#title = 'Silica Rejection',
  scene = list(xaxis=axx,yaxis=axy,zaxis=axz))
R_plot = R_plot %>% style(hovertemplate = paste('Rejection: %{z}',
                                                '<br> pH: %{x}',
                                                '<br> SiO2 concentration: %{y} mg/L'
                                                )
                          )

R_plot <- add_trace(
  p = R_plot,
  z = Rejection_lm_surface,
  x = axis_x,
  y = axis_y,
  type = "surface",
  colorbar = list(title = 'SiO<sub>2</sub> Rejection'),
  colorscale = 'magma',
  opacity=0.7
)

R_plot

```


### Silica as function of pH and Cl/SO4 ratio
```{R 3D Silica_pH_Cl_anion, echo=FALSE, message=FALSE, warning=FALSE, , echo=FALSE}

#SPRR_rejection <- na.omit((SPRR_data%>%filter(Stream == "Rejection")))

library(reshape2)



#Vores linear model:
Rejection_lm <- lm(Rej_SiO2 ~ pH + Cl_SO4,data=Ion_data_frame)
#Graph Resolution (more important for more complex shapes)
graph_reso <- 0.01

#Setup Axis
axis_x <- seq(min(Ion_data_frame$pH), max(Ion_data_frame$pH), by = graph_reso)
axis_y <- seq(min(Ion_data_frame$Cl_SO4), max(Ion_data_frame$Cl_SO4), by = graph_reso)

#Sample points
Rejection_lm_surface <- expand.grid(pH = axis_x,Cl_SO4 = axis_y,KEEP.OUT.ATTRS = F)
Rejection_lm_surface$Rej_SiO2 <- predict.lm(Rejection_lm, newdata = Rejection_lm_surface)
Rejection_lm_surface <- acast(Rejection_lm_surface, Cl_SO4 ~ pH, value.var = "Rej_SiO2") #y ~ x

axx <- list(
  title = "pH")
axy <- list(
  title = "Cl<sup>-</sup>/SO<sub>4</sub><sup>2-</sup> Ratio")
axz <- list(
  title = "SiO<sub>2</sub> Rejection [%]")

R_plot <- plot_ly(
 Ion_data_frame,
  x = ~ pH,
  y = ~ Cl_SO4,
  z = ~ Rej_SiO2,
  type = "scatter3d",
  mode = "markers",
  marker = list(
    color = ~ Rej_SiO2,
    colorscale = 'magma',
    line = list(
        color = 'rgb(0, 0, 0)',
        width = 1
    )
    )
)%>%layout(#title = 'Silica Rejection',
  scene = list(xaxis=axx,yaxis=axy,zaxis=axz)) %>% style(hovertemplate = paste('Rejection: %{z}',
                                                '<br> pH: %{x}',
                                                '<br> Cl/SO4:%{y}'
                                                )
                          )

R_plot <- add_trace(
  p = R_plot,
  z = Rejection_lm_surface,
  x = axis_x,
  y = axis_y,
  type = "surface",
  colorbar = list(title = 'SiO<sub>2</sub> Rejection'),
  colorscale = 'magma',
  opacity=0.7
)

R_plot

```



### Silica as function of Cl/SO4 ratio and silica concentration
```{R 3D Silica_Cl_anion_SiO2mmol, echo=FALSE, message=FALSE, warning=FALSE, , echo=FALSE}

#SPRR_rejection <- na.omit((SPRR_data%>%filter(Stream == "Rejection")))

library(reshape2)


#Vores linear model:
Rejection_lm <- lm(Rej_SiO2 ~ Cl_SO4 + SiO2_mmol,data=Ion_data_frame)
#Graph Resolution (more important for more complex shapes)
graph_reso <- 0.01

#Setup Axis
axis_x <- seq(min(Ion_data_frame$Cl_SO4), max(Ion_data_frame$Cl_SO4), by = graph_reso)
axis_y <- seq(min(Ion_data_frame$SiO2_mmol), max(Ion_data_frame$SiO2_mmol), by = graph_reso)

#Sample points
Rejection_lm_surface <- expand.grid(Cl_SO4 = axis_x,SiO2_mmol = axis_y,KEEP.OUT.ATTRS = F)
Rejection_lm_surface$Rej_SiO2 <- predict.lm(Rejection_lm, newdata = Rejection_lm_surface)
Rejection_lm_surface <- acast(Rejection_lm_surface, SiO2_mmol ~ Cl_SO4, value.var = "Rej_SiO2") #y ~ x


axx <- list(
  title = "Cl/SO4 Ratio")
axy <- list(
  title = "SiO<sub>2</sub> Concentration [mM]")
axz <- list(
  title = "SiO<sub>2</sub> Rejection [%]")

R_plot <- plot_ly(
 Ion_data_frame,
  x = ~ Cl_SO4,
  y = ~ SiO2_mmol,
  z = ~ Rej_SiO2,
  type = "scatter3d",
  mode = "markers",
  marker = list(
    color = ~ Rej_SiO2,
    colorscale = 'magma',
    line = list(
        color = 'rgb(0, 0, 0)',
        width = 1
    )
    )
)%>%layout(#title = 'Silica Rejection',
  scene = list(xaxis=axx,yaxis=axy,zaxis=axz))
R_plot = R_plot %>% style(hovertemplate = paste('Rejection: %{z}',
                                                '<br> Cl/SO4: %{x}',
                                                '<br> SiO2 concentration: %{y} mg/L'
                                                )
                          )

R_plot <- add_trace(
  p = R_plot,
  z = Rejection_lm_surface,
  x = axis_x,
  y = axis_y,
  type = "surface",
  colorbar = list(title = 'SiO<sub>2</sub> Rejection'),
  colorscale = 'magma',
  opacity=0.7
)

R_plot

```







# Cl rejection  {.tabset}
## 2D Multiple Linear Regression
We assume that pH does not play a significant role in Cl rejection, at least not to the same degree as for SiO2.
Instead the chemical environment i.e. which other species are present and in what amounts are theorized to have a greater influence.

We check if [Cl],[anion],[Cl]/[anion] has a significant role
Anion fraktion udregneds udfra Cl/[SO4]+[SiO2_ladet]+[Cl]

```{r Cl rejection against anion ration  , echo=FALSE}

ggplotly(ggplot(Ion_data_frame, aes(x=SO4_mmol, y=Rej_Cl,color=name))+geom_point())


###Different models ###

fit_Clrej_ratio= lm(Rej_Cl~Cl_SO4, data = Ion_data_frame)
ggplotRegression(fit_Clrej_ratio)
summary(fit_Clrej_ratio)

fit_Clrej_cl_anion = lm(Rej_Cl~Cl_anion, data = Ion_data_frame)
ggplotRegression(fit_Clrej_cl_anion)
summary(fit_Clrej_cl_anion)

fit_Clrej_so4 = lm(Rej_Cl~SO4_mmol, data = Ion_data_frame)
ggplotRegression(fit_Clrej_so4)
summary(fit_Clrej_so4)

fit_Clrej_cl_pH = lm(Rej_Cl~pH, data = Ion_data_frame)
ggplotRegression(fit_Clrej_cl_pH)
summary(fit_Clrej_cl_pH)

fit_Clrej_cl_sio2 = lm(Rej_Cl~SiO2_mmol, data = Ion_data_frame)
ggplotRegression(fit_Clrej_cl_sio2)
summary(fit_Clrej_cl_sio2)

#### Cl rejection multiple regression ####
fit_Clrej_multi = lm(Rej_Cl~SO4_mmol+total_sio2_ladet+Cl_mmol, data = Ion_data_frame)
summary(fit_Clrej_multi)
plot(fit_Clrej_multi)

plot(x=predict(fit_Clrej_multi), y=na.omit(Ion_data_frame$Rej_Cl),
     xlab='Predicted Values',
     ylab='Actual Values',
     main='Predicted vs. Actual Values',
     abline(a=0, b=1))



fit_Clrej_both_multi = lm(Rej_Cl~Cl_mmol*SO4_mmol*total_sio2_ladet, data = Ion_data_frame_both)
summary(fit_Clrej_both_multi)
plot(x=predict(fit_Clrej_both_multi), y=na.omit(Ion_data_frame_both$Rej_Cl),
     xlab='Predicted Values',
     ylab='Actual Values',
     main='Predicted vs. Actual Values',
     abline(a=0, b=1))


fit_Clrej_both_multi_best = lm(Rej_Cl~SO4_mmol+Cl_mmol+SiO2_mmol, data = Ion_data_frame_both)
summary(fit_Clrej_both_multi_best)
plot(x=predict(fit_Clrej_both_multi_best), y=na.omit(Ion_data_frame_both$Rej_Cl),
     xlab='Predicted Values',
     ylab='Actual Values',
     main='Predicted vs. Actual Values',
     abline(a=0, b=1))
```
Conclusion: [Cl] not useful to predict Rejection of Cl
neither is [anion] or [SO4]
[Cl]/[Anion] has a weak correlation to Rejection R2 0.53 (significant P>0.003)

[Cl/Anion]+pH R2 0.63 Cl/Anion P>0.00225 **,pH P>0.07329 . .

Removing the high SO4 point shows how wack the correlations otherwise are.



```{r fri leg, eval=FALSE, include=FALSE}
fit_Clrej_test1 = lm(Rej_Cl~SiO2_mmol, data = Ion_data_frame)
summary(fit_Clrej_test1)
ggplotRegression(fit_Clrej_test1)

plot(x=predict(fit_Clrej_test1), y=na.omit(Ion_data_frame$Rej_Cl),
     xlab='Predicted Values',
     ylab='Actual Values',
     main='Predicted vs. Actual Values',
     abline(a=0, b=1))

fit2 = lm(Rej_Cl~Cl_anion, data = Ion_data_frame%>%filter(state=="Steady State"))

#pred.int <- predict(model, interval = "prediction")
ggplotly(ggplot(Ion_data_frame, aes(x=SO4_mmol, y=Rej_Cl,color=name))+geom_point())

ggplotRegression(fit_Clrej_test1)

model = lm(Rej_Cl ~ 1, data=Ion_data_frame)
biggest <- formula(lm(Rej_Cl~.,Ion_data_frame))
fwd.model = step(model, direction='forward', scope=biggest)

test_data=Ion_data_frame[c(2,4,10,12),]
fit_test= lm(Rej_Cl~pH, data = test_data)
summary(fit_test)

plot(x=predict(fit_test), y=na.omit(test_data$Rej_Cl),
     xlab='Predicted Values',
     ylab='Actual Values',
     main='Predicted vs. Actual Values',
     abline(a=0, b=1))
ggplotRegression(fit_test)



```
## 3D Representation {.tabset}
### All Data Points
#### Cl rejection as function of Cl/SO4 ratio pH
```{r cl Cl/SO4 + pH, echo=FALSE}
#Ion_data_frame=Ion_data_frame[-1,] #Include to remove the point with high sulphate (NB! careful not to run line multiple times)




#Vores linear model:
Rejection_lm <- lm(Rej_Cl ~ Cl_SO4 + pH,data=Ion_data_frame)
#Graph Resolution (more important for more complex shapes)
graph_reso <- 0.01

#Setup Axis
axis_x <- seq(min(Ion_data_frame$Cl_SO4), max(Ion_data_frame$Cl_SO4), by = graph_reso)
axis_y <- seq(min(Ion_data_frame$pH), max(Ion_data_frame$pH), by = graph_reso)

#Sample points
Rejection_lm_surface <- expand.grid(Cl_SO4 = axis_x,pH = axis_y,KEEP.OUT.ATTRS = F)
Rejection_lm_surface$Rej_Cl <- predict.lm(Rejection_lm, newdata = Rejection_lm_surface)
Rejection_lm_surface <- acast(Rejection_lm_surface, pH ~ Cl_SO4, value.var = "Rej_Cl") #y ~ x


axx <- list(
  title = "Cl<sup>-</sup>/SO<sub>4</sub><sup>2-</sup> Ratio")
axy <- list(
  title = "pH")
axz <- list(
  title = "Cl<sup>-</sup> Rejection [%]")

R_plot <- plot_ly(
 Ion_data_frame,
  x = ~ Cl_SO4,
  y = ~ pH,
  z = ~ Rej_Cl,
  type = "scatter3d",
  mode = "markers",
  marker = list(
    color = ~ Rej_Cl,
    colorscale = 'magma',
    line = list(
        color = 'rgb(0, 0, 0)',
        width = 1
    )
    )
)%>%layout(#title = 'Chloride Rejection',
  scene = list(xaxis=axx,yaxis=axy,zaxis=axz))
R_plot = R_plot %>% style(hovertemplate = paste('Rejection: %{z}',
                                                '<br> Cl/SO4 ratio: %{x}',
                                                '<br> pH: %{y}'
                                                )
                          )

R_plot <- add_trace(
  p = R_plot,
  z = Rejection_lm_surface,
  x = axis_x,
  y = axis_y,
  type = "surface",
  colorbar = list(title = 'Cl<sup>-</sup> Rejection'),
  colorscale = 'magma',
  opacity=0.7
)

R_plot
```

#### Cl rejection as function of Cl/SO4 ratio and SiO2
```{r cl Cl/SO4 + [SiO2], echo=FALSE}




#Vores linear model:
Rejection_lm <- lm(Rej_Cl ~ Cl_SO4 + SiO2_mmol,data=Ion_data_frame)
#Graph Resolution (more important for more complex shapes)
graph_reso <- 0.01

#Setup Axis
axis_x <- seq(min(Ion_data_frame$Cl_SO4), max(Ion_data_frame$Cl_SO4), by = graph_reso)
axis_y <- seq(min(Ion_data_frame$SiO2_mmol), max(Ion_data_frame$SiO2_mmol), by = graph_reso)

#Sample points
Rejection_lm_surface <- expand.grid(Cl_SO4 = axis_x,SiO2_mmol = axis_y,KEEP.OUT.ATTRS = F)
Rejection_lm_surface$Rej_Cl <- predict.lm(Rejection_lm, newdata = Rejection_lm_surface)
Rejection_lm_surface <- acast(Rejection_lm_surface, SiO2_mmol ~ Cl_SO4, value.var = "Rej_Cl") #y ~ x

axx <- list(
  title = "Cl<sup>-</sup>/SO<sub>4</sub><sup>2-</sup> Ratio")
axy <- list(
  title = "SiO<sub>2</sub> Concentration [mM]")
axz <- list(
  title = "Cl<sup>-</sup> Rejection [%]")


R_plot <- plot_ly(
 Ion_data_frame,
  x = ~ Cl_SO4,
  y = ~ SiO2_mmol,
  z = ~ Rej_Cl,
  type = "scatter3d",
  mode = "markers",
  marker = list(
    color = ~ Rej_Cl,
    colorscale = 'magma',
    line = list(
        color = 'rgb(0, 0, 0)',
        width = 1
    )
    )
)%>%layout(#title = 'Chloride Rejection',
  scene = list(xaxis=axx,yaxis=axy,zaxis=axz))
R_plot = R_plot %>% style(hovertemplate = paste('Rejection: %{z}',
                                                '<br> Cl/SO4 ratio: %{x}',
                                                '<br> SiO2_mmol: %{y}'
                                                )
                          )

R_plot <- add_trace(
  p = R_plot,
  z = Rejection_lm_surface,
  x = axis_x,
  y = axis_y,
  type = "surface",
  colorbar = list(title = 'Cl<sup>-</sup> Rejection'),
  colorscale = 'magma',
  opacity=0.7
)

R_plot
```


#### Cl rejection as function of sio2 and pH
```{r cl SiO2 + pH, echo=FALSE}

#SPRR_rejection <- na.omit((SPRR_data%>%filter(Stream == "Rejection")))



#Vores linear model:
Rejection_lm <- lm(Rej_Cl ~ SiO2_mmol + pH,data=Ion_data_frame)
#Graph Resolution (more important for more complex shapes)
graph_reso <- 0.01

#Setup Axis
axis_x <- seq(min(Ion_data_frame$SiO2_mmol), max(Ion_data_frame$SiO2_mmol), by = graph_reso)
axis_y <- seq(min(Ion_data_frame$pH), max(Ion_data_frame$pH), by = graph_reso)

#Sample points
Rejection_lm_surface <- expand.grid(SiO2_mmol = axis_x,pH = axis_y,KEEP.OUT.ATTRS = F)
Rejection_lm_surface$Rej_Cl <- predict.lm(Rejection_lm, newdata = Rejection_lm_surface)
Rejection_lm_surface <- acast(Rejection_lm_surface, pH ~ SiO2_mmol, value.var = "Rej_Cl") #y ~ x

axx <- list(
  title = "SiO<sub>2</sub> Concentration [mM]")
axy <- list(
  title = "pH")
axz <- list(
  title = "Cl<sup>-</sup> Rejection [%]")

R_plot <- plot_ly(
 Ion_data_frame,
  x = ~ SiO2_mmol,
  y = ~ pH,
  z = ~ Rej_Cl,
  type = "scatter3d",
  mode = "markers",
  marker = list(
    color = ~ Rej_Cl,
    colorscale = 'magma',
    line = list(
        color = 'rgb(0, 0, 0)',
        width = 1
    )
    )
)%>%layout(#title = 'Chloride Rejection',
  scene = list(xaxis=axx,yaxis=axy,zaxis=axz))
R_plot = R_plot %>% style(hovertemplate = paste('Rejection: %{z}',
                                                '<br> SiO2 concentration: %{x}',
                                                '<br> pH: %{y}'
                                                )
                          )

R_plot <- add_trace(
  p = R_plot,
  z = Rejection_lm_surface,
  x = axis_x,
  y = axis_y,
  type = "surface",
  colorbar = list(title = 'Cl<sup>-</sup> Rejection'),
  colorscale = 'magma',
  opacity=0.7
)

R_plot
```


### Removing of two outliers
#### Cl rejection as function of Cl/SO4 ratio pH
```{r cl Cl/SO4 + pH both, echo=FALSE}
#Ion_data_frame=Ion_data_frame[-1,] #Include to remove the point with high sulphate (NB! careful not to run line multiple times)




#Vores linear model:
Rejection_lm <- lm(Rej_Cl ~ Cl_SO4 + pH,data=Ion_data_frame)
#Graph Resolution (more important for more complex shapes)
graph_reso <- 0.01

#Setup Axis
axis_x <- seq(min(Ion_data_frame$Cl_SO4), max(Ion_data_frame$Cl_SO4), by = graph_reso)
axis_y <- seq(min(Ion_data_frame$pH), max(Ion_data_frame$pH), by = graph_reso)

#Sample points
Rejection_lm_surface <- expand.grid(Cl_SO4 = axis_x,pH = axis_y,KEEP.OUT.ATTRS = F)
Rejection_lm_surface$Rej_Cl <- predict.lm(Rejection_lm, newdata = Rejection_lm_surface)
Rejection_lm_surface <- acast(Rejection_lm_surface, pH ~ Cl_SO4, value.var = "Rej_Cl") #y ~ x


R_plot <- plot_ly(
 Ion_data_frame,
  x = ~ Cl_SO4,
  y = ~ pH,
  z = ~ Rej_Cl,
  type = "scatter3d",
  mode = "markers",
  marker = list(
    color = ~ Rej_Cl,
    colorscale = 'magma',
    line = list(
        color = 'rgb(0, 0, 0)',
        width = 1
    )
    )
)%>%layout(title = 'Chloride Rejection')
R_plot = R_plot %>% style(hovertemplate = paste('Rejection: %{z}',
                                                '<br> Cl/SO4 ratio: %{x}',
                                                '<br> pH: %{y}'
                                                )
                          )

R_plot <- add_trace(
  p = R_plot,
  z = Rejection_lm_surface,
  x = axis_x,
  y = axis_y,
  type = "surface",
  colorbar = list(title = 'Cl Rejection'),
  colorscale = 'magma',
  opacity=0.7
)

R_plot
```

#### Cl rejection as function of Cl/SO4 ratio and SiO2
```{r cl Cl/SO4 + [SiO2] both, echo=FALSE}




#Vores linear model:
Rejection_lm <- lm(Rej_Cl ~ Cl_SO4 + SiO2_mmol,data=Ion_data_frame)
#Graph Resolution (more important for more complex shapes)
graph_reso <- 0.01

#Setup Axis
axis_x <- seq(min(Ion_data_frame$Cl_SO4), max(Ion_data_frame$Cl_SO4), by = graph_reso)
axis_y <- seq(min(Ion_data_frame$SiO2_mmol), max(Ion_data_frame$SiO2_mmol), by = graph_reso)

#Sample points
Rejection_lm_surface <- expand.grid(Cl_SO4 = axis_x,SiO2_mmol = axis_y,KEEP.OUT.ATTRS = F)
Rejection_lm_surface$Rej_Cl <- predict.lm(Rejection_lm, newdata = Rejection_lm_surface)
Rejection_lm_surface <- acast(Rejection_lm_surface, SiO2_mmol ~ Cl_SO4, value.var = "Rej_Cl") #y ~ x


R_plot <- plot_ly(
 Ion_data_frame,
  x = ~ Cl_SO4,
  y = ~ SiO2_mmol,
  z = ~ Rej_Cl,
  type = "scatter3d",
  mode = "markers",
  marker = list(
    color = ~ Rej_Cl,
    colorscale = 'magma',
    line = list(
        color = 'rgb(0, 0, 0)',
        width = 1
    )
    )
)%>%layout(title = 'Chloride Rejection')
R_plot = R_plot %>% style(hovertemplate = paste('Rejection: %{z}',
                                                '<br> Cl/SO4 ratio: %{x}',
                                                '<br> SiO2_mmol: %{y}'
                                                )
                          )

R_plot <- add_trace(
  p = R_plot,
  z = Rejection_lm_surface,
  x = axis_x,
  y = axis_y,
  type = "surface",
  colorbar = list(title = 'Cl Rejection'),
  colorscale = 'magma',
  opacity=0.7
)

R_plot
```


#### Cl rejection as function of sio2 and pH
```{r cl SiO2 + pH both, echo=FALSE}

#SPRR_rejection <- na.omit((SPRR_data%>%filter(Stream == "Rejection")))



#Vores linear model:
Rejection_lm <- lm(Rej_Cl ~ SiO2_mmol + pH,data=Ion_data_frame)
#Graph Resolution (more important for more complex shapes)
graph_reso <- 0.01

#Setup Axis
axis_x <- seq(min(Ion_data_frame$SiO2_mmol), max(Ion_data_frame$SiO2_mmol), by = graph_reso)
axis_y <- seq(min(Ion_data_frame$pH), max(Ion_data_frame$pH), by = graph_reso)

#Sample points
Rejection_lm_surface <- expand.grid(SiO2_mmol = axis_x,pH = axis_y,KEEP.OUT.ATTRS = F)
Rejection_lm_surface$Rej_Cl <- predict.lm(Rejection_lm, newdata = Rejection_lm_surface)
Rejection_lm_surface <- acast(Rejection_lm_surface, pH ~ SiO2_mmol, value.var = "Rej_Cl") #y ~ x


R_plot <- plot_ly(
 Ion_data_frame,
  x = ~ SiO2_mmol,
  y = ~ pH,
  z = ~ Rej_Cl,
  type = "scatter3d",
  mode = "markers",
  marker = list(
    color = ~ Rej_Cl,
    colorscale = 'magma',
    line = list(
        color = 'rgb(0, 0, 0)',
        width = 1
    )
    )
)%>%layout(title = 'Chloride Rejection')
R_plot = R_plot %>% style(hovertemplate = paste('Rejection: %{z}',
                                                '<br> SiO2 concentration: %{x}',
                                                '<br> pH: %{y}'
                                                )
                          )

R_plot <- add_trace(
  p = R_plot,
  z = Rejection_lm_surface,
  x = axis_x,
  y = axis_y,
  type = "surface",
  colorbar = list(title = 'Cl Rejection'),
  colorscale = 'magma',
  opacity=0.7
)

R_plot
```

